Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-15 writeup/cover_letter.tex
tweaked cover letter

\documentclass[11pt]{letter}
\usepackage[hidelinks]{hyperref}
\usepackage[green]{msuletterhead}
%\topmarginskip{-0.35in}
%\bottommarginskip{-1.5in}
%\leftmarginsize{1in}
%\rightmarginsize{1.25in}
%\sigskipbefore{0.4in}
%\sigskipafter{0in}
%\noLines
%\nolines
%\noHeadline
%\noheadline
%\signature{Gideon Bradburd, Graham Coop, and Peter Ralph}
%
%\namefrom{}
%\addrfrom{Gideon Bradburd \\ Dept. of Integrative Biology \\ Michigan State University \\ East Lansing, MI 48823 USA \\ 
%\href{mailto:bradburd@msu.edu}{bradburd@msu.edu}}
%\emailfrom{bradburd@msu.edu}
%
%\greetto{To the Editor(s) --}
%\closeline{Sincerely,}

\begin{document}
%\begin{newlfm}

@@

In the manuscript, we present a novel statistical method 
for the simultaneous inference of continuous and discrete patterns of population structure.
The method estimates ancestry proportions for each 
sample from a set of discrete population layers, 
and, within each layer, estimates a rate at which relatedness decays with distance.
This model explicitly addresses the ``clines vs. clusters" problem in 
modeling population genetic variation by jointly accommodating 
continuous and discrete patterns of differentiation. 
We demonstrate the utility of this approach using simulations 
and two empirical applications. %, with datasets from poplars and black bears. 
We also release an associated R package, called \texttt{conStruct}, 
for ``\emph{con}tinuous \emph{struct}ure."

@@

As of this submission, \texttt{STRUCTURE} alone has been cited more than 20,000 times.
However, as the costs of sequencing continue to fall
and good geospatial information becomes more readily available,
the limitations we cite above will become more severe.
Our method has the potential to fill this gap.
% We therefore believe that our work represents an important and timely contribution to the field.

@@

Sincerely,
Gideon Bradburd, 
Graham Coop, and 
Peter Ralph
%\end{newlfm}
\end{document}

%What is the scientific question you are addressing?
%What is the key finding that answers this question?
%What is the nature of the evidence you provide in support of your conclusion?
%What are the three most recently published articles that are relevant to this question?
%What significance do your results have for the field?
%What significance do your results have for the broader community (of biologists and/or the public)?
%What other novel findings do you present?
%Is there additional information that we should take into account?

>>>>

\documentclass[11pt]{letter}
\usepackage[hidelinks]{hyperref}
\usepackage[green]{msuletterhead}
\begin{document}

@@

In the manuscript, we present a novel statistical method 
for the simultaneous inference of continuous and discrete patterns of population structure.
The method estimates ancestry proportions for each 
sample from a set of discrete population layers, 
and, within each layer, estimates a rate at which relatedness decays with distance.
This model explicitly addresses the ``clines vs. clusters" problem in 
modeling population genetic variation by jointly accommodating 
continuous and discrete patterns of differentiation. 
We demonstrate the utility of this approach using simulations 
and two empirical applications.
We also release an associated R package, called \texttt{conStruct}, 
for ``\emph{con}tinuous \emph{struct}ure."

@@

As of this submission, \texttt{STRUCTURE} alone has been cited more than 20,000 times.
However, as the costs of sequencing continue to fall
and good geospatial information becomes more readily available,
the limitations we cite above will become more severe.
Our method provides an important extension to \texttt{STRUCTURE} and similar approaches, 
one that solves a critical and widely known basic conceptual drawback of the model. 
We therefore believe that our work represents an 
important and timely contribution to the field.

@@

Sincerely,
Gideon Bradburd, 
Graham Coop, and 
Peter Ralph
\end{document}
